 # Install and load necessary packages
# Install and load necessary packages
install.packages("sf")
library(sf)

---
title: "ENVS363/563.3 Computational Essay"
output:
  quarto::quarto_html:
    toc: true
---

# Part 1 – Common

## 1.1 Collecting and Importing the Data

### 1.1.1 Import and Explore Airbnb Data

```{r}

# Load Airbnb data for San Francisco
sf_airbnb <- read.csv("sf.csv")

# Load Airbnb data for San Mateo
sm_airbnb <- read.csv("sm.csv")

# Load Airbnb data for Oakland
oak_airbnb <- read.csv("oak.csv")
# Display a summary of the datasets
summary(sf_airbnb)
summary(sm_airbnb)
summary(oak_airbnb)

```
```{r}
# Replace 'path/to/sf_1.0-15.zip' with the actual path where you saved the ZIP file
install.packages("sf_1.0-15.zip", repos = NULL, type = "win.binary")
library(sf)

# Load GeoJSON data for San Francisco neighborhoods
sf_neighborhoods <- st_read("sf.geojson")

# Load GeoJSON data for San Mateo neighborhoods
sm_neighborhoods <- st_read("sm.geojson")

# Load GeoJSON data for Oakland neighborhoods
oak_neighborhoods <- st_read("oak.geojson")
```
```{r}
# Install and load necessary packages for data manipulation and visualization
install.packages(c("dplyr", "ggplot2"))
library(dplyr)
library(ggplot2)

# Combine neighborhood and Airbnb data for each location
sf_combined <- left_join(sf_neighborhoods, sf_airbnb, by = c("neighbourhood" = "neighbourhood"))
sm_combined <- left_join(sm_neighborhoods, sm_airbnb, by = c("neighbourhood" = "neighbourhood"))
oak_combined <- left_join(oak_neighborhoods, oak_airbnb, by = c("neighbourhood" = "neighbourhood"))

# Visualize the average Airbnb prices by neighborhood
ggplot(sf_combined, aes(fill = price, color = price)) +
  geom_sf() +
  scale_fill_gradient(low = "lightblue", high = "darkblue") +
  scale_color_gradient(low = "lightblue", high = "darkblue") +
  labs(title = "Average Airbnb Prices in San Francisco Neighborhoods")
  ```
  ````{r}
  ggplot(sm_combined, aes(fill = price, color = price)) +
  geom_sf() +
  scale_fill_gradient(low = "lightgreen", high = "red") +
  scale_color_gradient(low = "lightgreen", high = "red") +
  labs(title = "Average Airbnb Prices in San Mateo Neighborhoods")
  ggplot(oak_combined, aes(fill = price, color = price)) +
  geom_sf() +
  scale_fill_gradient(low = "lightcoral", high = "darkred") +
  scale_color_gradient(low = "lightcoral", high = "darkred") +
  labs(title = "Average Airbnb Prices in Oakland Neighborhoods")
    